Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-19 paper.tex
Discuss possible extension in conclusion

>>>>

One obvious extension of our method would be to exploit redundancy not just between contexts of parent and child goals, but also between those of siblings or even unrelated goals.
The forward state supports this since any two goals can be diffed and the old goal's forward state updated to match the new one's context.
